---
title: "hw4"
output: html_document
---
## About the homework 4
The task this week is to:

Read in [global gender inequality data](http://hdr.undp.org/en/indicators/68606#)  
Join the global gender inequality index to spatial data of the [World](https://hub.arcgis.com/datasets/2b93b06dc0dc4e809d3c8db5cb96ba69_0/explore?location=-0.133762%2C0.000000%2C1.00), creating a new column of difference in inequality between 2010 and 2019  
Share it with the World on GitHub  
Add you repository URL to the circulated spreadsheet  

## 1. Load library 
```{r}
library(sf)
library(sp)
library(tidyverse)
library(janitor)
library(here)
library(ggplot2)
library(here)
library(rgdal)
library(tmap)
library(RSQLite)
library(countrycode)
```

## 2. Load gender inequality csv 

```{r}
gender <- read_csv(here::here('data',
                        'Gender Inequality Index (GII).csv'),
                   locale = locale(encoding = 'latin1'), skip=5,na='..')
```

## 3. Load world spatial data

```{r}
world <- st_read(here("Data", 
                      "World_Countries_(Generalized)", 
                      "World_Countries__Generalized_.shp"))
```
## 4. Data manipulation 
* create a new variable contains country, 2019, 2010 data  
* calculate the difference between 2010-2019  
* create a new column contains countrycode so that can be joined to world spatial data

```{r}
genderDiffer <- gender %>% 
  clean_names() %>% 
  select(country,x2019,x2010) %>% 
  mutate(differ=x2019-x2010) %>% 
  slice(1:189,) %>% 
  mutate(iso_code=countrycode(country,
                              origin ='country.name', destination = 'iso2c' ))
```

* join csv to spatial data  
```{r}
genderJoin <- world %>% 
  clean_names() %>% 
  left_join(., genderDiffer,
            by=c('aff_iso' = 'iso_code'))
```

## 5. Plot map 
```{r}
tmap_mode('plot')
qtm(genderJoin,
    fill='x2010')
qtm(genderJoin,
    fill='x2019')
qtm(genderJoin,
    fill='differ')

```


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
